---
title: "**Code**"
subtitle: "Specifically code we have looked at during club sessions"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```
<br>

# Session 3

Covered:

* basic R code and syntax, incl. vectors and different classes of data
* intro to logical subsetting
* functions and use in statistics
* ugly plots (for future comparison purposes)

```{r}
1+1

2+2

variable <- 2

class(name)

c <- "word"

class(c)

vector <- c(1, 2, 3, 4)

vector2 <- c("one", "two", "three", "four")

vector[2]

vector[3]

vector[4]

vector1 <- c(1, 2, 3, 4)

vector <- c("one", "one", "one")

vector <- c('one', 'one')

length(vector1)

vector2 <- c(1, 2)

length(vector2)

#a caveat of R 
cbind(vector1, vector2)

mean(vector1)

median(vector1)
```

```{r, echo = TRUE, eval = TRUE}
x <- c(1, 2, 3, 4)
y <- c(2, 3, 4, 5)

plot(x, y)

hist(x)

barplot(x)
```

# Holidays

* Watch the introduction to working with data video [here](https://www.youtube.com/watch?v=RtV0Ne__r2k&t=131s&ab_channel=Ciu).

# Cleaning data (preprocessing)

Covered:

* the dplyr package and its 'verbs'

```{r}

```

# Using ggplot2

Covered:

* syntax and structure of using ggplot2 to create better visualisations of data

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```
