---
title: "**Some advanced EDA examples**"
subtitle: "Extending what we have covered in class"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: yeti
---

```{css, echo=FALSE}
pre {
  max-height: 800px;
  overflow-y: auto;
}

pre[class] {
  max-height: 800px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





<br>


# Example 1
<br>

* This first example utilises a dataset consisting of real road crashes in Victoria obtained from the [CrashStats datasets provided by VicRoads](https://discover.data.vic.gov.au/dataset/crash-stats-data-extract). The CrashStats data allows us to analyse serious vehicle crashes based on time, location, conditions, crash type, road user type, object hit etc.

* The code below has some wrangling, and then the plots are stored as objects. 

<br>

```{r, echo = FALSE, eval = TRUE, message = FALSE, include = FALSE}
library(tidyverse)
                                                                  library(formattable)
                                                                  library(kableExtra)
                                                                  library(ggthemr)
                                                                  library(chron)
                                                                  library(dplyr)
                                                                  library(caret)
                                                                  library(scales)
                                                                  library(lubridate)
                                                                  ggthemr('fresh')
                                                                  
                                                                  train <- read.csv('VicRoadFatalData.csv')
                                                                  
                                                                  train <- train %>%
                                                                    mutate_if(is.character, as.factor)
                                                                  
                                                                  
                                                                  train$ACCIDENTDATE <- as.Date(as.character(train$ACCIDENTDATE), format = "%Y-%m-%d")
                                                                  
                                                                  train$ACCIDENTTIME <- times(as.character(train$ACCIDENTTIME)) 
                                                                  
                                                                  train$OWNER_POSTCODE <- as.factor(train$OWNER_POSTCODE)
                                                                  
                                                                  train$TOTAL_NO_OCCUPANTS <- as.integer(train$TOTAL_NO_OCCUPANTS)
                                                                  
                                                                  train <- train %>%
                                                                    filter(TOTAL_NO_OCCUPANTS > 0)
                                                                  
                                                                  train$occ_group <- as.factor(ifelse(train$TOTAL_NO_OCCUPANTS <= 7, train$TOTAL_NO_OCCUPANTS, "7+"))
                                                                  
                                                                  age_counts <- train %>%
                                                                    group_by(Age.Group, SEX) %>%
                                                                    summarise(non_fatal = sum(fatal == 0), fatal = sum(fatal == 1))
                                                                  
                                                                  # Calculate the proportion of fatal crashes within each age group
                                                                  age_counts$proportion <- age_counts$fatal / (age_counts$fatal + age_counts$non_fatal)
                                                                  
                                                                  age_counts$proportion <- round(age_counts$proportion,5)
                                                                  
                                                                  age_counts
                                                                  age_counts$merged <- ifelse(age_counts$SEX == "M",
                                                                                              paste(age_counts$Age.Group, "", sep = ""),
                                                                                              paste(age_counts$Age.Group, "", sep = " "))
                                                                  
                                                                  age_counts_long <- age_counts %>%
                                                                    pivot_longer(cols = c(non_fatal, fatal, proportion), names_to = "Crash_Status", values_to = "Count")
                                                                  
                                                                  library(scales)
                                                                  
                                                                  age_gender_plot <- ggplot(filter(age_counts_long, SEX != "U"), aes(x = factor(merged), y = Count, fill = interaction(Crash_Status, as.integer(factor(merged)) %% 2))) +
                                                                    geom_bar(stat = "identity", just = -0.15, width = 0.8) +
                                                                    geom_text(aes(label = ifelse(Crash_Status == "proportion", gsub("%", "", scales::percent(Count, accuracy = 0.1)), ""),
                                                                                  y = Count,
                                                                                  group = Crash_Status),
                                                                              position = position_stack(vjust = 0.5, reverse = TRUE),
                                                                              color = "violetred1",
                                                                              size = 3.3,
                                                                              vjust = -0.5,
                                                                              hjust = -0.3) +
                                                                    xlab("Age group (years)") +
                                                                    scale_y_continuous(breaks = c(0, 5000, 10000, 15000, 20000, 25000),
                                                                                       labels = scales::comma) +
                                                                    expand_limits(y = c(0, 25500)) +
                                                                    ylab("Number of car crashes") +
                                                                    ggtitle("Chart 1: Distribution of car crashes by age and gender") +
                                                                    theme(text = element_text(size = 12)) +
                                                                    theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
                                                                          axis.title.x = element_text(hjust = 0.5),
                                                                          axis.title.y = element_text(hjust = 0.5)) +
                                                                    scale_x_discrete(breaks = (unique(filter(age_counts_long, SEX != "U")$merged)[c(seq(1,29,2))])) +
                                                                    scale_fill_manual(name = "Crash Status",
                                                                                      breaks = c("fatal.1", "non_fatal.1", "non_fatal.0", "proportion.0", "proportion.1"),
                                                                                      labels = c("Fatal (%)", "Non-fatal (M)", "Non-fatal (F)", "", ""),
                                                                                      values = c("violetred1", "steelblue3", "palegreen3", "white", "white", "violetred1"),
                                                                                      na.value = "violetred1")
                                                                  
                                                                  helment <- train %>%
                                                                    group_by(HELMET_BELT_WORN) %>%
                                                                    summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))
                                                                  
                                                                  helment$proportion = helment$fatal_count / (helment$fatal_count + helment$non_fatal_count)
                                                                  
                                                                  helment$proportion = round(helment$proportion, 3)
                                                                  
                                                                  helmet <- helment %>%
                                                                    pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = "Crash_Status", values_to = "Count")
                                                                  
                                                                  helmet <- ggplot(filter(helmet, HELMET_BELT_WORN != "Other"), aes(x = factor(HELMET_BELT_WORN), y = Count, fill = Crash_Status)) +
                                                                    geom_bar(stat = "identity") +
                                                                    geom_text(aes(label = ifelse(Crash_Status == "proportion", gsub("%", "", scales::percent(Count, accuracy = 0.1)), ""),
                                                                                  y = Count,
                                                                                  group = Crash_Status),
                                                                              position = position_stack(vjust = 0.5, reverse = TRUE),
                                                                              color = "violetred1",
                                                                              size = 4,
                                                                              vjust = -0.8) +
                                                                    xlab("Seatbelt status") +
                                                                    ylab("Number of car crashes") +
                                                                    scale_y_continuous(breaks = c(0, 50000, 100000, 150000),
                                                                                       labels = scales::comma) +
                                                                    expand_limits(y = c(0, 160000)) +
                                                                    ggtitle("Chart 2: Distribution of\ncar crashes by seatbelt status") +
                                                                    theme(text = element_text(size = 12)) +
                                                                    theme(plot.title = element_text(size = 12,
                                                                                                    face = "bold", 
                                                                                                    hjust = 0.5), 
                                                                          axis.title.x = element_text(hjust = 0.5), 
                                                                          axis.title.y = element_text(hjust = 0.5)) +
                                                                    scale_fill_manual(name = "Crash Status", 
                                                                                      labels = c("Fatal (%)", "Non-fatal", ""), 
                                                                                      values = c("violetred1","steelblue","white"))
                                                                  
                                                                  train$acc_year = format(as.Date(train$ACCIDENTDATE), "%Y")
                                                                  
                                                                  train$acc_month = format(as.Date(train$ACCIDENTDATE), "%m")
                                                                  train$acc_month <- as.factor(train$acc_month)
                                                                  month_names <- month.name
                                                                  
                                                                  # Assign each level of train$acc_month to the corresponding month name
                                                                  levels(train$acc_month) <- month_names
                                                                  
                                                                  # Print the updated factor variable
                                                                  train$acc_month
                                                                  
                                                                  #create age groups for vehicles 
                                                                  
                                                                  train$vehicle_age <- as.integer(as.integer(train$acc_year) + 1 - train$VEHICLE_YEAR_MANUF)
                                                                  
                                                                  train$v_age_group <- cut(train$vehicle_age, breaks = c(0, 2, 5, 10, 15, 20, 60), labels = c("0-2", "2-5", "5-10", "10-15", "15-20", "20+"))
                                                                  
                                                                  vaged <- train %>%
                                                                    group_by(v_age_group) %>%
                                                                    summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))
                                                                  
                                                                  vaged$proportion = vaged$fatal_count / (vaged$fatal_count + vaged$non_fatal_count)
                                                                  
                                                                  vaged$proportion = round(vaged$proportion, 3)
                                                                  
                                                                  vaged <- vaged %>%
                                                                    pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = "Crash_Status", values_to = "Count")
                                                                  
                                                                  vaged <- na.omit(vaged)
                                                                  
                                                                  veh_age_plot <- ggplot(vaged, aes(x = factor(v_age_group), y = Count, fill = Crash_Status)) +
                                                                    geom_bar(stat = "identity") +
                                                                    geom_text(aes(label = ifelse(Crash_Status == "proportion", gsub("%", "", scales::percent(Count, accuracy = 0.1)), ""),
                                                                                  y = Count,
                                                                                  group = Crash_Status),
                                                                              position = position_stack(vjust = 0.5, reverse = TRUE),
                                                                              color = "violetred1",
                                                                              size = 4,
                                                                              vjust = -0.8) +
                                                                    xlab("Vehicle age group (years)") +
                                                                    ylab("Number of car crashes") +
                                                                    scale_y_continuous(breaks = c(0, 20000, 40000),
                                                                                       labels = scales::comma) +
                                                                    expand_limits(y = c(0, 60000)) +
                                                                    ggtitle("Chart 4: Distribution of car\ncrashes by vehicle age group") +
                                                                    theme(text = element_text(size = 12)) +
                                                                    theme(plot.title = element_text(size = 12,
                                                                                                    face = "bold", 
                                                                                                    hjust = 0.5), 
                                                                          axis.title.x = element_text(hjust = 0.5), 
                                                                          axis.title.y = element_text(hjust = 0.5)) +
                                                                    scale_fill_manual(name = "Crash Status", 
                                                                                      labels = c("Fatal (%)", "Non-fatal", ""), 
                                                                                      values = c("violetred1","steelblue","white"))
                                                                  
                                                                  vtype <- train %>%
                                                                    group_by(VEHICLE_TYPE) %>%
                                                                    summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))
                                                                  
                                                                  vtype$proportion <- vtype$fatal_count / (vtype$fatal_count + vtype$non_fatal_count)
                                                                  
                                                                  vtype$proportion <- round(vtype$proportion, 3)
                                                                  
                                                                  vtype <- vtype %>%
                                                                    pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = "Crash_Status", values_to = "Count")
                                                                  
                                                                  # Update the ggplot code
                                                                  vehicle <- ggplot(vtype, aes(x = factor(VEHICLE_TYPE), y = Count, fill = Crash_Status)) +
                                                                    geom_bar(stat = "identity") +
                                                                    geom_text(aes(label = ifelse(Crash_Status == "proportion", gsub("%", "", scales::percent(Count, accuracy = 0.1)), ""),
                                                                                  y = Count,
                                                                                  group = Crash_Status),
                                                                              position = position_stack(vjust = 0.5, reverse = TRUE),
                                                                              color = "violetred1",
                                                                              size = 4,
                                                                              vjust = -0.8) +
                                                                    xlab("Vehicle type") +
                                                                    ylab("Number of car crashes") +
                                                                    scale_y_continuous(breaks = c(0, 40000, 80000, 120000),
                                                                                       labels = scales::comma) +
                                                                    expand_limits(y = c(0, 140000)) +
                                                                    ggtitle("Chart 3: Distribution of\ncar crashes by vehicle type") +
                                                                    theme(text = element_text(size = 12)) +
                                                                    theme(plot.title = element_text(size = 12,
                                                                                                    face = "bold",
                                                                                                    hjust = 0.5),
                                                                          axis.title.x = element_text(hjust = 0.5),
                                                                          axis.title.y = element_text(hjust = 0.5),
                                                                          axis.text.x = element_text(angle = 45, hjust = 1)) +
                                                                    scale_fill_manual(name = "Crash Status",
                                                                                      labels = c("Fatal (%)", "Non-fatal", ""),
                                                                                      values = c("violetred1", "steelblue", "white")) +
                                                                    scale_x_discrete(labels = c(levels(vtype$VEHICLE_TYPE)[1], "Heavy Vehicle", levels(vtype$VEHICLE_TYPE)[3:4], "Single Trailer", levels(vtype$VEHICLE_TYPE)[6:8]))
                                                                  
                                                                  occupants <- train %>%
                                                                    group_by(occ_group) %>%
                                                                    summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))
                                                                  
                                                                  occupants$proportion <- occupants$fatal_count / (occupants$fatal_count + occupants$non_fatal_count)
                                                                  
                                                                  occupants$proportion <- round(occupants$proportion, 3)
                                                                   
                                                                  occupants <- occupants %>%
                                                                    pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = "Crash_Status", values_to = "Count")
                                                                  
                                                                  occupantg <- ggplot(occupants, aes(x = factor(occ_group), y = Count, fill = Crash_Status)) +
                                                                    geom_bar(stat = "identity") +
                                                                    geom_text(aes(label = ifelse(Crash_Status == "proportion", gsub("%", "", scales::percent(Count, accuracy = 0.1)), ""),
                                                                                  y = Count,
                                                                                  group = Crash_Status),
                                                                              position = position_stack(vjust = 0.5, reverse = TRUE),
                                                                              color = "violetred1",
                                                                              size = 4,
                                                                              vjust = -0.8) +
                                                                    xlab("Number of occupants") +
                                                                    ylab("Number of car crashes") +
                                                                    scale_y_continuous(labels = scales::comma) +
                                                                    expand_limits(y = c(0, 160000)) +
                                                                    theme(plot.title = element_text(size = 12,
                                                                                                    face = "bold",
                                                                                                    hjust = 0.5),
                                                                          axis.title.x = element_text(hjust = 0.5),
                                                                          axis.title.y = element_text(hjust = 0.5),
                                                                          axis.text.x = element_text(size = 12, hjust = 1)) +
                                                                    scale_fill_manual(name = "Crash Status",
                                                                                      labels = c("Fatal (%)", "Non-fatal", ""),
                                                                                      values = c("violetred1", "steelblue", "white")) +
                                                                    ggtitle("Chart 5: Distribution of\ncar crashes by occupants") +
                                                                    theme(text = element_text(size = 12)) +
                                                                    theme(plot.title = element_text(size = 12,
                                                                                                    face = "bold", 
                                                                                                    hjust = 0.5), 
                                                                          axis.title.x = element_text(hjust = 0.5), 
                                                                          axis.title.y = element_text(hjust = 0.5)) 
                                                                  
                                                                  
                                                                  train$hour <- as.integer(format(strptime(train$ACCIDENTTIME, format = "%H:%M:%S"), format = "%H"))
                                                                  
                                                                  hourly <- train %>%
                                                                    group_by(hour) %>%
                                                                    summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))
                                                                  
                                                                  hourly$proportion <- hourly$fatal_count / (hourly$fatal_count + hourly$non_fatal_count)
                                                                  
                                                                  hourly$proportion <- round(hourly$proportion, 3)
                                                                  
                                                                  hourly <- hourly %>%
                                                                    pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = "Crash_Status", values_to = "Count")
                                                                  
                                                                  train$hour <- as.numeric(train$hour)  # Convert hour to numeric if it's not already
                                                                  
                                                                  train$h_block <- cut(train$hour, breaks = c(-1, 2, 5, 8, 12, 15, 18, 21, 24),
                                                                                       labels = c("12:00AM-2:59AM", "3:00AM-5:59AM", "6:00AM-8:59AM", "9:00AM-11:59AM",
                                                                                                  "12:00PM-2:59PM", "3:00PM-5:59PM", "6:00PM-8:59PM", "9:00PM-11:59PM"),
                                                                                       include.lowest = TRUE)
                                                                  
                                                                  
                                                                  h_prop <- train %>%
                                                                    group_by(h_block, DAY_OF_WEEK) %>%
                                                                    summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))
                                                                  
                                                                  h_prop$proportion <- h_prop$fatal_count / (h_prop$fatal_count + h_prop$non_fatal_count)
                                                                  
                                                                  summary_table_count <- train %>% group_by(h_block, DAY_OF_WEEK) %>% summarise(Count = n())
                                                                  
                                                                  summary_table_prop <- train %>% group_by(h_block, DAY_OF_WEEK) %>% summarise(Count =n())
                                                                  
                                                                  summary_table_prop <- aggregate(fatal ~ h_block + DAY_OF_WEEK, data = train, FUN = function(x) sum(x) / length(x))
                                                                  
                                                                  weekday_order <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
                                                                  h_prop$DAY_OF_WEEK <- factor(h_prop$DAY_OF_WEEK, levels = weekday_order)
                                                                  summary_table_count$DAY_OF_WEEK <- factor(summary_table_count$DAY_OF_WEEK, levels = weekday_order)
                                                                  
                                                                  
                                                                  weekday_levels <- c("Mon", "Tues", "Wed", "Thur", "Fri", "Sat", "Sun")
                                                                  
                                                                  levels(h_prop$DAY_OF_WEEK) <- weekday_levels
                                                                  
                                                                  levels(summary_table_count$DAY_OF_WEEK) <- weekday_levels
                                                                  
                                                                  
                                                                  # Create the plot for total proportion of 1s
                                                                  fataltime <- ggplot(h_prop, aes(y = h_block, x = DAY_OF_WEEK, fill = proportion)) +
                                                                    geom_tile() +
                                                                    scale_fill_gradient(low = "white", high = "red", labels = scales::percent_format()) +
                                                                    labs(x = "", y = "", fill = "Fatal proportion") +
                                                                    scale_x_discrete(position = "top") +
                                                                    theme(legend.position = "bottom") +
                                                                    ggtitle("Chart 7: Fatal proportion of\naccidents by time & day of week") +
                                                                    theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
                                                                          axis.title.x = element_text(hjust = 0.5),
                                                                          axis.title.y = element_text(hjust = 0.5),
                                                                          axis.text.x = element_text(angle = 0, size = 12), 
                                                                          axis.text.y = element_text(size = 15),
                                                                          legend.position = "bottom",
                                                                          legend.text = element_text(size = 15),
                                                                          legend.title = element_text(size = 12)) +
                                                                    guides(fill = guide_colorbar(title.position = "top", title.hjust = 0.5, barwidth = 10))
                                                                  
                                                                  voltime <- ggplot(summary_table_count, aes(y = h_block, x = DAY_OF_WEEK, fill = Count)) +
                                                                    geom_tile() +
                                                                    scale_fill_gradient(low = "white", high = "steelblue", labels = scales::comma_format()) +
                                                                    labs(x = "", y = "", fill = "Number of accidents") +
                                                                    scale_x_discrete(position = "top") +
                                                                    ggtitle("Chart 6: Number of accidents\nby time & day of week") +
                                                                    theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
                                                                          axis.title.x = element_text(hjust = 0.5),
                                                                          axis.title.y = element_text(hjust = 0.5),
                                                                          axis.text.x = element_text(angle = 0, size = 12), 
                                                                          axis.text.y = element_text(size = 15),
                                                                          legend.position = "bottom",
                                                                          legend.text = element_text(size = 12),
                                                                          legend.title = element_text(size = 12)) +
                                                                    guides(fill = guide_colorbar(title.position = "top", title.hjust = 0.5, barwidth = 10))
                                                                  
                                                                  
                                                                  train$speed_g <- cut(train$SPEED_ZONE, 
                                                                                       breaks = c(40, 60, 90, Inf), 
                                                                                       labels = c("40-60", "70-90", "100+"),
                                                                                       include.lowest = TRUE)
                                                                  
                                                                  road_geom <- train %>%
                                                                    group_by(ROAD_GEOMETRY, speed_g) %>%
                                                                    summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))
                                                                  
                                                                  road_geom$proportion = road_geom$fatal_count / (road_geom$fatal_count + road_geom$non_fatal_count)
                                                                  
                                                                  road_geom$proportion = round(road_geom$proportion, 3)
                                                                  
                                                                  road_geom <- road_geom %>%
                                                                    pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = "Crash_Status", values_to = "Count")
                                                                  
                                                                  road_geom <- as.data.frame(road_geom)
                                                                  
                                                                  road_geom$ROAD_GEOMETRY <- factor(road_geom$ROAD_GEOMETRY, 
                                                                                                    levels = c("Cross intersection", "Not at intersection", "T intersection", "Other"))
                                                                  
                                                                  road_geom$Count <- ifelse(road_geom$ROAD_GEOMETRY == "Other", 0, road_geom$Count)
                                                                  
                                                                  # Sample data for text labels
                                                                  labels_df <- data.frame(
                                                                    speed_g = c("40-60", "40-60", "40-60", "70-90", "70-90", "70-90", "100+", "100+", "100+"),
                                                                    ROAD_GEOMETRY = c("Cross intersection", "Not at intersection", "T intersection",
                                                                                      "Cross intersection", "Not at intersection", "T intersection",
                                                                                      "Cross intersection", "Not at intersection", "T intersection"),
                                                                    y_labels = c("0.7", "1.1", "0.5", "1.4", "2.1", "1.1", "5.3", "5.7", "4.7"),
                                                                    Count = c(15000, 55000, 95000, 7000, 25000, 46000, 5000, 15000, 27000),
                                                                    stringsAsFactors = FALSE
                                                                  )
                                                                  
                                                                  road_g <- ggplot(road_geom, aes(x = speed_g, y = as.numeric(Count), fill = as.factor(ROAD_GEOMETRY))) +
                                                                    geom_bar(stat = "identity") +
                                                                    xlab("Speed zone group (km/h)") +
                                                                    ylab("Number of car crashes") +
                                                                    scale_y_continuous(labels = scales::comma) +
                                                                    theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
                                                                          axis.title.x = element_text(hjust = 0.5),
                                                                          axis.title.y = element_text(hjust = 0.5),
                                                                          axis.text.x = element_text(size = 12)) +
                                                                    ggtitle("Chart 8: Distribution of car crashes\nby speed zone and road geometry") +
                                                                    theme(text = element_text(size = 12)) +
                                                                    theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5), 
                                                                          axis.title.x = element_text(hjust = 0.5), 
                                                                          axis.title.y = element_text(hjust = 0.5)) +
                                                                    scale_fill_manual(name = "Road geometry",
                                                                                      labels = c("Cross intersection", "Not at intersection", "T intersection", "\nNote: \nFatal proportions\nshown in white (%)"),
                                                                                      values = c("maroon3", "steelblue", "palegreen3", "white")) +
                                                                    geom_text(data = labels_df, aes(label = y_labels), color = "white", fontface = "bold", size = 4)
``` 


```{r, echo = TRUE, eval = FALSE}
library(tidyverse)
library(formattable)
library(kableExtra)
library(ggthemr)
library(chron)
library(dplyr)
library(caret)
library(scales)
library(lubridate)
ggthemr('fresh')

train <- read.csv('VicRoadFatalData.csv')

train <- train %>%
  mutate_if(is.character, as.factor)


train$ACCIDENTDATE <- as.Date(as.character(train$ACCIDENTDATE), format = '%Y-%m-%d')

train$ACCIDENTTIME <- times(as.character(train$ACCIDENTTIME)) 

train$OWNER_POSTCODE <- as.factor(train$OWNER_POSTCODE)

train$TOTAL_NO_OCCUPANTS <- as.integer(train$TOTAL_NO_OCCUPANTS)

train <- train %>%
  filter(TOTAL_NO_OCCUPANTS > 0)

train$occ_group <- as.factor(ifelse(train$TOTAL_NO_OCCUPANTS <= 7, train$TOTAL_NO_OCCUPANTS, '7+'))

age_counts <- train %>%
  group_by(Age.Group, SEX) %>%
  summarise(non_fatal = sum(fatal == 0), fatal = sum(fatal == 1))

# Calculate the proportion of fatal crashes within each age group
age_counts$proportion <- age_counts$fatal / (age_counts$fatal + age_counts$non_fatal)

age_counts$proportion <- round(age_counts$proportion,5)

#age_counts
age_counts$merged <- ifelse(age_counts$SEX == 'M',
                            paste(age_counts$Age.Group, '', sep = ''),
                            paste(age_counts$Age.Group, '', sep = ' '))

age_counts_long <- age_counts %>%
  pivot_longer(cols = c(non_fatal, fatal, proportion), names_to = 'Crash_Status', values_to = 'Count')

library(scales)

age_gender_plot <- ggplot(filter(age_counts_long, SEX != 'U'), aes(x = factor(merged), y = Count, fill = interaction(Crash_Status, as.integer(factor(merged)) %% 2))) +
  geom_bar(stat = 'identity', just = -0.15, width = 0.8) +
  geom_text(aes(label = ifelse(Crash_Status == 'proportion', gsub('%', '', scales::percent(Count, accuracy = 0.1)), ''),
                y = Count,
                group = Crash_Status),
            position = position_stack(vjust = 0.5, reverse = TRUE),
            color = 'violetred1',
            size = 4.2,
            vjust = -0.5,
            hjust = -0.3) +
  xlab('Age group (years)') +
  scale_y_continuous(breaks = c(0, 5000, 10000, 15000, 20000, 25000),
                     labels = scales::comma) +
  expand_limits(y = c(0, 25500)) +
  ylab('Number of car crashes') +
  ggtitle('Chart 1: Distribution of car crashes by age and gender') +
  theme(text = element_text(size = 12)) +
  theme(plot.title = element_text(size = 12, face = 'bold', hjust = 0.5),
        axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5)) +
  scale_x_discrete(breaks = (unique(filter(age_counts_long, SEX != 'U')$merged)[c(seq(1,29,2))])) +
  scale_fill_manual(name = 'Crash Status',
                    breaks = c('fatal.1', 'non_fatal.1', 'non_fatal.0', 'proportion.0', 'proportion.1'),
                    labels = c('Fatal (%)', 'Non-fatal (M)', 'Non-fatal (F)', '', ''),
                    values = c('violetred1', 'steelblue3', 'palegreen3', 'white', 'white', 'violetred1'),
                    na.value = 'violetred1')

helment <- train %>%
  group_by(HELMET_BELT_WORN) %>%
  summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))

helment$proportion = helment$fatal_count / (helment$fatal_count + helment$non_fatal_count)

helment$proportion = round(helment$proportion, 3)

helmet <- helment %>%
  pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = 'Crash_Status', values_to = 'Count')

helmet <- ggplot(filter(helmet, HELMET_BELT_WORN != 'Other'), aes(x = factor(HELMET_BELT_WORN), y = Count, fill = Crash_Status)) +
  geom_bar(stat = 'identity') +
  geom_text(aes(label = ifelse(Crash_Status == 'proportion', gsub('%', '', scales::percent(Count, accuracy = 0.1)), ''),
                y = Count,
                group = Crash_Status),
            position = position_stack(vjust = 0.5, reverse = TRUE),
            color = 'violetred1',
            size = 4,
            vjust = -0.8) +
  xlab('Seatbelt status') +
  ylab('Number of car crashes') +
  scale_y_continuous(breaks = c(0, 50000, 100000, 150000),
                     labels = scales::comma) +
  expand_limits(y = c(0, 160000)) +
  ggtitle('Chart 2: Distribution of\ncar crashes by seatbelt status') +
  theme(text = element_text(size = 12)) +
  theme(plot.title = element_text(size = 12,
                                  face = 'bold', 
                                  hjust = 0.5), 
        axis.title.x = element_text(hjust = 0.5), 
        axis.title.y = element_text(hjust = 0.5)) +
  scale_fill_manual(name = 'Crash Status', 
                    labels = c('Fatal (%)', 'Non-fatal', ''), 
                    values = c('violetred1','steelblue','white'))

train$acc_year = format(as.Date(train$ACCIDENTDATE), '%Y')

train$acc_month = format(as.Date(train$ACCIDENTDATE), '%m')
train$acc_month <- as.factor(train$acc_month)
month_names <- month.name

# Assign each level of train$acc_month to the corresponding month name
levels(train$acc_month) <- month_names

# Print the updated factor variable
#train$acc_month

#create age groups for vehicles 

train$vehicle_age <- as.integer(as.integer(train$acc_year) + 1 - train$VEHICLE_YEAR_MANUF)

train$v_age_group <- cut(train$vehicle_age, breaks = c(0, 2, 5, 10, 15, 20, 60), labels = c('0-2', '2-5', '5-10', '10-15', '15-20', '20+'))

vaged <- train %>%
  group_by(v_age_group) %>%
  summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))

vaged$proportion = vaged$fatal_count / (vaged$fatal_count + vaged$non_fatal_count)

vaged$proportion = round(vaged$proportion, 3)

vaged <- vaged %>%
  pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = 'Crash_Status', values_to = 'Count')

vaged <- na.omit(vaged)

veh_age_plot <- ggplot(vaged, aes(x = factor(v_age_group), y = Count, fill = Crash_Status)) +
  geom_bar(stat = 'identity') +
  geom_text(aes(label = ifelse(Crash_Status == 'proportion', gsub('%', '', scales::percent(Count, accuracy = 0.1)), ''),
                y = Count,
                group = Crash_Status),
            position = position_stack(vjust = 0.5, reverse = TRUE),
            color = 'violetred1',
            size = 4,
            vjust = -0.8) +
  xlab('Vehicle age group (years)') +
  ylab('Number of car crashes') +
  scale_y_continuous(breaks = c(0, 20000, 40000),
                     labels = scales::comma) +
  expand_limits(y = c(0, 60000)) +
  ggtitle('Chart 4: Distribution of car\ncrashes by vehicle age group') +
  theme(text = element_text(size = 12)) +
  theme(plot.title = element_text(size = 12,
                                  face = 'bold', 
                                  hjust = 0.5), 
        axis.title.x = element_text(hjust = 0.5), 
        axis.title.y = element_text(hjust = 0.5)) +
  scale_fill_manual(name = 'Crash Status', 
                    labels = c('Fatal (%)', 'Non-fatal', ''), 
                    values = c('violetred1','steelblue','white'))

vtype <- train %>%
  group_by(VEHICLE_TYPE) %>%
  summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))

vtype$proportion <- vtype$fatal_count / (vtype$fatal_count + vtype$non_fatal_count)

vtype$proportion <- round(vtype$proportion, 3)

vtype <- vtype %>%
  pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = 'Crash_Status', values_to = 'Count')

# Update the ggplot code
vehicle <- ggplot(vtype, aes(x = factor(VEHICLE_TYPE), y = Count, fill = Crash_Status)) +
  geom_bar(stat = 'identity') +
  geom_text(aes(label = ifelse(Crash_Status == 'proportion', gsub('%', '', scales::percent(Count, accuracy = 0.1)), ''),
                y = Count,
                group = Crash_Status),
            position = position_stack(vjust = 0.5, reverse = TRUE),
            color = 'violetred1',
            size = 4,
            vjust = -0.8) +
  xlab('Vehicle type') +
  ylab('Number of car crashes') +
  scale_y_continuous(breaks = c(0, 40000, 80000, 120000),
                     labels = scales::comma) +
  expand_limits(y = c(0, 140000)) +
  ggtitle('Chart 3: Distribution of\ncar crashes by vehicle type') +
  theme(text = element_text(size = 12)) +
  theme(plot.title = element_text(size = 12,
                                  face = 'bold',
                                  hjust = 0.5),
        axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(name = 'Crash Status',
                    labels = c('Fatal (%)', 'Non-fatal', ''),
                    values = c('violetred1', 'steelblue', 'white')) +
  scale_x_discrete(labels = c(levels(vtype$VEHICLE_TYPE)[1], 'Heavy Vehicle', levels(vtype$VEHICLE_TYPE)[3:4], 'Single Trailer', levels(vtype$VEHICLE_TYPE)[6:8]))

occupants <- train %>%
  group_by(occ_group) %>%
  summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))

occupants$proportion <- occupants$fatal_count / (occupants$fatal_count + occupants$non_fatal_count)

occupants$proportion <- round(occupants$proportion, 3)

occupants <- occupants %>%
  pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = 'Crash_Status', values_to = 'Count')

occupantg <- ggplot(occupants, aes(x = factor(occ_group), y = Count, fill = Crash_Status)) +
  geom_bar(stat = 'identity') +
  geom_text(aes(label = ifelse(Crash_Status == 'proportion', gsub('%', '', scales::percent(Count, accuracy = 0.1)), ''),
                y = Count,
                group = Crash_Status),
            position = position_stack(vjust = 0.5, reverse = TRUE),
            color = 'violetred1',
            size = 4,
            vjust = -0.8) +
  xlab('Number of occupants') +
  ylab('Number of car crashes') +
  scale_y_continuous(labels = scales::comma) +
  expand_limits(y = c(0, 160000)) +
  theme(plot.title = element_text(size = 12,
                                  face = 'bold',
                                  hjust = 0.5),
        axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text.x = element_text(size = 12, hjust = 1)) +
  scale_fill_manual(name = 'Crash Status',
                    labels = c('Fatal (%)', 'Non-fatal', ''),
                    values = c('violetred1', 'steelblue', 'white')) +
  ggtitle('Chart 5: Distribution of\ncar crashes by occupants') +
  theme(text = element_text(size = 12)) +
  theme(plot.title = element_text(size = 12,
                                  face = 'bold', 
                                  hjust = 0.5), 
        axis.title.x = element_text(hjust = 0.5), 
        axis.title.y = element_text(hjust = 0.5)) 


train$hour <- as.integer(format(strptime(train$ACCIDENTTIME, format = '%H:%M:%S'), format = '%H'))

hourly <- train %>%
  group_by(hour) %>%
  summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))

hourly$proportion <- hourly$fatal_count / (hourly$fatal_count + hourly$non_fatal_count)

hourly$proportion <- round(hourly$proportion, 3)

hourly <- hourly %>%
  pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = 'Crash_Status', values_to = 'Count')

train$hour <- as.numeric(train$hour)  # Convert hour to numeric if it's not already

train$h_block <- cut(train$hour, breaks = c(-1, 2, 5, 8, 12, 15, 18, 21, 24),
                     labels = c('12:00AM-2:59AM', '3:00AM-5:59AM', '6:00AM-8:59AM', '9:00AM-11:59AM',
                                '12:00PM-2:59PM', '3:00PM-5:59PM', '6:00PM-8:59PM', '9:00PM-11:59PM'),
                     include.lowest = TRUE)


h_prop <- train %>%
  group_by(h_block, DAY_OF_WEEK) %>%
  summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))

h_prop$proportion <- h_prop$fatal_count / (h_prop$fatal_count + h_prop$non_fatal_count)

summary_table_count <- train %>% group_by(h_block, DAY_OF_WEEK) %>% summarise(Count = n())

summary_table_prop <- train %>% group_by(h_block, DAY_OF_WEEK) %>% summarise(Count =n())

summary_table_prop <- aggregate(fatal ~ h_block + DAY_OF_WEEK, data = train, FUN = function(x) sum(x) / length(x))

weekday_order <- c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday')
h_prop$DAY_OF_WEEK <- factor(h_prop$DAY_OF_WEEK, levels = weekday_order)
summary_table_count$DAY_OF_WEEK <- factor(summary_table_count$DAY_OF_WEEK, levels = weekday_order)


weekday_levels <- c('Mon', 'Tues', 'Wed', 'Thur', 'Fri', 'Sat', 'Sun')

levels(h_prop$DAY_OF_WEEK) <- weekday_levels

levels(summary_table_count$DAY_OF_WEEK) <- weekday_levels


# Create the plot for total proportion of 1s
fataltime <- ggplot(h_prop, aes(y = h_block, x = DAY_OF_WEEK, fill = proportion)) +
  geom_tile() +
  scale_fill_gradient(low = 'white', high = 'red', labels = scales::percent_format()) +
  labs(x = '', y = '', fill = 'Fatal proportion') +
  scale_x_discrete(position = 'top') +
  theme(legend.position = 'bottom') +
  ggtitle('Chart 7: Fatal proportion of\naccidents by time & day of week') +
  theme(plot.title = element_text(size = 12, face = 'bold', hjust = 0.5),
        axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 0, size = 12), 
        axis.text.y = element_text(size = 15),
        legend.position = 'bottom',
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 12)) +
  guides(fill = guide_colorbar(title.position = 'top', title.hjust = 0.5, barwidth = 10))

voltime <- ggplot(summary_table_count, aes(y = h_block, x = DAY_OF_WEEK, fill = Count)) +
  geom_tile() +
  scale_fill_gradient(low = 'white', high = 'steelblue', labels = scales::comma_format()) +
  labs(x = '', y = '', fill = 'Number of accidents') +
  scale_x_discrete(position = 'top') +
  ggtitle('Chart 6: Number of accidents\nby time & day of week') +
  theme(plot.title = element_text(size = 12, face = 'bold', hjust = 0.5),
        axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 0, size = 12), 
        axis.text.y = element_text(size = 15),
        legend.position = 'bottom',
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12)) +
  guides(fill = guide_colorbar(title.position = 'top', title.hjust = 0.5, barwidth = 10))


train$speed_g <- cut(train$SPEED_ZONE, 
                     breaks = c(40, 60, 90, Inf), 
                     labels = c('40-60', '70-90', '100+'),
                     include.lowest = TRUE)

road_geom <- train %>%
  group_by(ROAD_GEOMETRY, speed_g) %>%
  summarise(fatal_count = sum(fatal == TRUE), non_fatal_count = sum(fatal == FALSE))

road_geom$proportion = road_geom$fatal_count / (road_geom$fatal_count + road_geom$non_fatal_count)

road_geom$proportion = round(road_geom$proportion, 3)

road_geom <- road_geom %>%
  pivot_longer(cols = c(non_fatal_count, fatal_count, proportion), names_to = 'Crash_Status', values_to = 'Count')

road_geom <- as.data.frame(road_geom)

road_geom$ROAD_GEOMETRY <- factor(road_geom$ROAD_GEOMETRY, 
                                  levels = c('Cross intersection', 'Not at intersection', 'T intersection', 'Other'))

road_geom$Count <- ifelse(road_geom$ROAD_GEOMETRY == 'Other', 0, road_geom$Count)

# Sample data for text labels
labels_df <- data.frame(
  speed_g = c('40-60', '40-60', '40-60', '70-90', '70-90', '70-90', '100+', '100+', '100+'),
  ROAD_GEOMETRY = c('Cross intersection', 'Not at intersection', 'T intersection',
                    'Cross intersection', 'Not at intersection', 'T intersection',
                    'Cross intersection', 'Not at intersection', 'T intersection'),
  y_labels = c('0.7', '1.1', '0.5', '1.4', '2.1', '1.1', '5.3', '5.7', '4.7'),
  Count = c(15000, 55000, 95000, 7000, 25000, 46000, 5000, 15000, 27000),
  stringsAsFactors = FALSE
)

road_g <- ggplot(road_geom, aes(x = speed_g, y = as.numeric(Count), fill = as.factor(ROAD_GEOMETRY))) +
  geom_bar(stat = 'identity') +
  xlab('Speed zone group (km/h)') +
  ylab('Number of car crashes') +
  scale_y_continuous(labels = scales::comma) +
  theme(plot.title = element_text(size = 12, face = 'bold', hjust = 0.5),
        axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text.x = element_text(size = 12)) +
  ggtitle('Chart 8: Distribution of car crashes\nby speed zone and road geometry') +
  theme(text = element_text(size = 12)) +
  theme(plot.title = element_text(size = 12, face = 'bold', hjust = 0.5), 
        axis.title.x = element_text(hjust = 0.5), 
        axis.title.y = element_text(hjust = 0.5)) +
  scale_fill_manual(name = 'Road geometry',
                    labels = c('Cross intersection', 'Not at intersection', 'T intersection', '\nNote: \nFatal proportions\nshown in white (%)'),
                    values = c('maroon3', 'steelblue', 'palegreen3', 'white')) +
  geom_text(data = labels_df, aes(label = y_labels), color = 'white', fontface = 'bold', size = 4)
```
<br>

# Example 1 (plots)
<br>
```{r, eval = TRUE, echo = FALSE}
age_gender_plot
```
<br>
Analysis 

<br>
```{r, eval = TRUE, echo = F}
helmet
```
<br>
Analysis 

<br>
```{r, eval = TRUE, echo = F}
veh_age_plot
```
<br>
Analysis 

<br>
```{r, eval = TRUE, echo = F}
vehicle
```
<br>
Analysis 

<br>
```{r, eval = TRUE, echo = F}
occupantg
```
<br>
Analysis 

<br>
```{r, eval = TRUE, echo = F}
fataltime
```
<br>
Analysis 

<br>
```{r, eval = TRUE, echo = F}
voltime
```
<br>
Analysis

<br>
```{r, eval = TRUE, echo = F}
road_g
```
<br>
Analysis

<br>
<br>
<br>
<br>
<br>
<br>

# Example 2 - plotly examples

```{r, message = FALSE}
library(plotly)
library(htmlwidgets)

combi <- read.csv("Melbourne_housing_data_cleaned.csv")

# Create a correlation matrix
correlation_matrix <- cor(combi[, c("Price", "Rooms", "Bathroom", "Car", "Landsize")])

# Create an interactive heatmap
heatmap <- plot_ly(z = correlation_matrix, x = colnames(correlation_matrix), y = colnames(correlation_matrix), 
                   type = "heatmap", colorscale = "RdYlBu")

# Customize the layout
layout <- list(
  title = "Interactive Heatmap of Correlations",
  xaxis = list(tickangle = 45),
  yaxis = list(tickangle = 45)
)

# Create and display the interactive plot
plot_heatmap <- heatmap %>% layout(layout)

saveWidget(plot_heatmap, file = "heatmap.html")

```

<div style="position: relative; width: 100%; height: 0; padding-top: 56.2500%;
 padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden;
 border-radius: 8px; will-change: transform;">
 <iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;"
    src="heatmap.html" allow="fullscreen">
  </iframe>
</div>

</br>

```{r, message = FALSE, warning = FALSE}
library(plotly)

# Assuming your dataset is named 'combi'
# Group data by CouncilArea and calculate the count of properties
council_area_data <- combi %>% 
  group_by(CouncilArea) %>% 
  summarize(Count = n())

# Create a sunburst plot
sunburst_plot <- plot_ly(
  ids = council_area_data$CouncilArea,
  labels = council_area_data$CouncilArea,
  parents = "",
  values = council_area_data$Count,
  type = 'sunburst'
)

# Customize the sunburst plot
sunburst_plot <- sunburst_plot %>%
  layout(
    margin = list(l = 0, r = 0, b = 0, t = 0),
    sunburstcolors = colorRamp(c("lightblue", "blue"))
  )

# Create and display the interactive sunburst plot

saveWidget(sunburst_plot, file = "sunburst.html")

```

<div style="position: relative; width: 100%; height: 0; padding-top: 56.2500%;
 padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden;
 border-radius: 8px; will-change: transform;">
 <iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;"
    src="sunburst.html" allow="fullscreen">
  </iframe>
</div>


# Example 2
<br>

* This second example utilises the Melbourne housing market dataset. Note the code below does not include the pre-processing stage, which is necessary as the raw data from Kaggle has missing values. 
* It utilises interactive map libraries

<br>
```{r}
library(leaflet)
library(htmlwidgets)

melb <- read.csv("Melbourne_housing_data_cleaned.csv")

melb$Price <- as.character(melb$Price)

# Define a color palette
colors <- colorRampPalette(c("lightblue", "navy"))  # Adjust the color range as needed

library(leaflet)
library(RColorBrewer)  # You'll need this package for color scales

# Assuming you have a dataset 'melb' with columns 'Longitude' and 'Latitude'
# Convert the 'Price' column to character
melb$Price <- as.numeric(melb$Price)

# Define a color palette
library(leaflet)

# Define a custom color palette for Price
# Define the number of color steps and labels you want
library(leaflet)

# Define a custom color palette for Price
custom_palette <- colorNumeric(
  palette = c("steelblue2", "white"),  # Your custom colors for low and high values
  domain = melb$Price
)

# Create the map
m <- leaflet(melb) %>%
   addTiles(urlTemplate = "https://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}.png") %>%
  addCircleMarkers(
    lng = ~Longitude,
    lat = ~Latitude,
    popup = ~Price,
    radius = 3,
    color = ~custom_palette(Price)) %>%
    addLegend("bottomright", pal = custom_palette, values = ~Price,
    title = "Price (AUD)",
    labFormat = labelFormat(prefix = "$"),
    opacity = 1)

# Save the Leaflet map as an HTML widget
saveWidget(m, file = "leaflet_map.html")

```

<div style="position: relative; width: 100%; height: 0; padding-top: 56.2500%;
 padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden;
 border-radius: 8px; will-change: transform;">
 <iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;"
    src="leaflet_map.html" allow="fullscreen">
  </iframe>
</div>



<br>
<br>
<br>
<br>
<br>
<br>

# Example 3
<br>

* This slideshow contains visualisations created using two datasets. The first is the Melbourne housing market dataset. The second is [cash rate data from the RBA](https://www.rba.gov.au/statistics/cash-rate/). The rationale for using the cash rate data was to overlay the time series analysis of property sales. 

* Some of the interactive plots were creating using tableaeu, but you can mimick them with the interactive plot techniques we have introduced

<div style="position: relative; width: 100%; height: 0; padding-top: 56.2500%;
 padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden;
 border-radius: 8px; will-change: transform;">
  <iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;"
    src="https:&#x2F;&#x2F;www.canva.com&#x2F;design&#x2F;DAFxgC0YEks&#x2F;view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">
  </iframe>
</div>
<a href="https:&#x2F;&#x2F;www.canva.com&#x2F;design&#x2F;DAFxgC0YEks&#x2F;view?utm_content=DAFxgC0YEks&amp;utm_campaign=designshare&amp;utm_medium=embeds&amp;utm_source=link" target="_blank" rel="noopener">Melbourne Housing Pack [EDA version]</a> 


</br>
</br>
</br>
</br>


# Template title

* Template video [here](https://www.youtube.com/watch?v=RtV0Ne__r2k&t=131s&ab_channel=Ciu).





